Network Cascades

### 2016-08-26 paper/paper.tex
Change subtitle to something sensible
Add concrete abstract

\title{Network Cascades}
\subtitle{WattsApp With Those}
\author{Marco Brack \and Carsten Hartenfels}
\maketitle

\begin{abstract}
Concrete.
\end{abstract}

>>>>

\title{Network Cascades}
\subtitle{Watts' Simple Global Cascade Model}
\author{Marco Brack \and Carsten Hartenfels}
\maketitle

\begin{abstract}
Network cascades can be used to model social phenomena propagation, such as the uptake in use of communication technologies.

The paper ``A simple model of global cascades on random networks'' by Duncan J. Watts provides a way to model these kinds of cascades on random graphs. From this model, constraint conditions for the success of global cascades can be extracted.

We give an overview of the model combined with high-level, real world examples. The mathematical properties and findings of Watts' model are explained in detail. We also give the paper a treatment in regards to limitations and threats to validity, which the original does not mention about itself.
\end{abstract}
